---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pokepackage

<!-- badges: start -->
<!-- badges: end -->
The goal of pokepackage is to provide tools to enhance Pokémon data, including boosting stats, updating abilities, and preparing for battles.

## Installation

You can install the development version of pokepackage from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("tomh1988-8/pokepackage")
```

## Example
Below are examples demonstrating the main functionality of pokepackage:

### Boost Pokémon Stats with pokehack
This function boosts the stats of a specified Pokémon by 10%:
```{r}
library(pokepackage)
library(dplyr)

# Example Pokémon data
pokemon <- data.frame(
  name = c("Bulbasaur", "Charmander", "Squirtle"),
  defense = c(49, 43, 65),
  sp_attack = c(65, 60, 50),
  sp_defense = c(65, 50, 64),
  speed = c(45, 65, 43)
)

# Boost Bulbasaur's stats
pokemon <- pokehack("Bulbasaur", pokemon)
print(pokemon)

```

### Update Pokémon Abilities with pokeskill
This function allows updating or adding new abilities to one or more Pokémon:
```{r}
library(pokepackage)
library(dplyr)

# Add abilities to Bulbasaur and Charmander
pokemon <- data.frame(
  name = c("Bulbasaur", "Charmander", "Squirtle"),
  abilities = c("[Overgrow]", "[Blaze]", "[Torrent]")
)

pokemon <- pokeskill(
  pokemon = c("Bulbasaur", "Charmander"),
  new_skills = c("Solar Beam", "Inferno"),
  data = pokemon
)
print(pokemon)

```

### Train Pokémon with poketrain
This function trains six selected Pokémon, decreasing their weight and increasing their experience growth:
```{r}
library(pokepackage)
library(dplyr)

# Train six Pokémon
pokemon <- data.frame(
  name = c("Bulbasaur", "Charmander", "Squirtle", "Pikachu", "Jigglypuff", "Meowth"),
  weight_kg = c(6.9, 8.5, 9.0, 6.0, 5.5, 4.2),
  experience_growth = c(100, 120, 110, 95, 85, 80)
)

trained_pokemon <- poketrain(
  selected_pokemon = c("Bulbasaur", "Charmander", "Squirtle", "Pikachu", "Jigglypuff", "Meowth"),
  data = pokemon
)
print(trained_pokemon)

```

### Notes
Ensure all required libraries (dplyr, etc.) are loaded within the package or session.
Handle input errors gracefully. For example, invalid Pokémon names will result in error messages.
